Fusing Filters with Integer Linear Programming

### 2014-05-14 2014betterfusionforfilters/section/05-Benchmarks.tex
talk about stream fusion clustering in eg of normalize2 program

Note that, in the objective function, the weights for $x_{sum1, sum2}$ and $x_{sum2, ys1}$ are both only 1.
This is because they do not share any input arrays.

@@

A minimal solution to this is
\begin{tabbing}
MMMMMMMMMMMMMMMMMMMMMMMMMM \= M \= \kill
$x_{sum1, gts}, x_{sum1, sum2}, x_{ys1,  ys2}$
    \> $=$ \> $0$ \\
$x_{sum1, ys2}, x_{gts, ys1 }, x_{sum2, ys1}$
    \> $=$ \> $1$ \\
\\
$\pi_{sum1}, \pi_{gts }, \pi_{sum2}$
    \> $=$ \> $0$ \\
$\pi_{ys1 }, \pi_{ys2 }$
    \> $=$ \> $1$ \\
\\
$c_{gts}, c_{ys1}, c_{ys2}$           
    \> $=$ \> $0$ \\
\end{tabbing}
Looking at just the non-zero variables in the objective function,
$25 \cdot x_{sum1,ys2} + 25 \cdot x_{gts,ys1} + 1 \cdot x_{sum2, ys1} = 51$.
It is worth noting that, for example, the objective could be reduced by fusing $x_{sum1,ys2}$ together.
However, this conflicts with other constraints. Since $x_{sum1, sum2} = 0$, the constraint requires that $\pi_{sum1} = \pi_{sum2}$, and another constraint requires $\pi_{sum2} < \pi_{ys2}$.
These constraints may not all hold, so a clustering that fused sum1 and ys2 together would not allow sum1 and sum2 to be fused together.

>>>>

Note that, in the objective function, the weights for $x_{sum1, sum2}$ and $x_{sum2, ys1}$ are both only 1, because they do not share any input arrays.

@@

A minimal solution to this is
\begin{tabbing}
MMMMMMMMMMMMMMMMMMMMMMMMMM \= M \= \kill
$x_{sum1, gts}, x_{sum1, sum2}, x_{gts, sum2}, x_{ys1,  ys2}$
    \> $=$ \> $0$ \\
$x_{sum1, ys2}, x_{gts, ys1 }, x_{sum2, ys1}$
    \> $=$ \> $1$ \\
\\
$\pi_{sum1}, \pi_{gts }, \pi_{sum2}$
    \> $=$ \> $0$ \\
$\pi_{ys1 }, \pi_{ys2 }$
    \> $=$ \> $1$ \\
\\
$c_{gts}, c_{ys1}, c_{ys2}$           
    \> $=$ \> $0$ \\
\end{tabbing}
Looking at just the non-zero variables in the objective function, the value is
$25 \cdot x_{sum1,ys2} + 25 \cdot x_{gts,ys1} + 1 \cdot x_{sum2, ys1} = 51$.
It is worth noting that, for example, the objective could be reduced by fusing $x_{sum1,ys2}$ together.
However, this conflicts with other constraints. Since $x_{sum1, sum2} = 0$, the constraint requires that $\pi_{sum1} = \pi_{sum2}$, and another constraint requires $\pi_{sum2} < \pi_{ys2}$.
These constraints may not all hold, so a clustering that fused sum1 and ys2 together would not allow sum1 and sum2 to be fused together.

We can also calculate the objective function for the clustering used by stream fusion, to contrast and show that the constraints are valid.
To do this, the values of $x_{ij}$ variables are:
\begin{tabbing}
MMMMMMMMMMMMMMMMMMMMMMMMMM \= M \= \kill
$x_{gts, sum2}$
    \> $=$ \> $0$ \\
$x_{sum1, gts}, x_{sum1, sum2}, x_{ys1,  ys2}, x_{sum1, ys2}, x_{gts, ys1 }, x_{sum2, ys1}$
    \> $=$ \> $1$ \\
\end{tabbing}
If we add these extra equality constraints to the integer linear program and solve it, one possible solution is:
\begin{tabbing}
MMMMMMMMMMMMMMMMMMMMMMMMMM \= M \= \kill
$\pi_{sum1}, \pi_{gts }, \pi_{sum2}$
    \> $=$ \> $0$ \\
$\pi_{ys1 }, \pi_{ys2 }$
    \> $=$ \> $1$ \\
\\
$c_{gts}, c_{ys1}, c_{ys2}$           
    \> $=$ \> $0$ \\
\end{tabbing}
It is interesting to note that two nodes having equal $\pi_i$ values does not imply that the two nodes are fused together.
Conversely, however, different $\pi_i$ values do imply that two nodes are not fused together.

The objective function for this solution is
$25 \cdot x_{sum1, gts} + 1 \cdot x_{sum1,sum2} + 25 \cdot x_{sum1, ys2} + 25 \cdot x_{gts, ys1} + 1 \cdot x_{sum2, ys1} + 25 \cdot x_{ys1, ys2} = 102$.
